Aligning marine species range data to better serve science and conservation

### 2016-02-01 data_explore/data_prep.Rmd
updating species area calculations with the latest and greatest species list

spp_list <- spp_list %>%
  mutate(sm_perc = ifelse(!is.na(sm_perc), 0, sm_perc))
  # filter(!is.na(sm_perc)) %>%
  ### will ditch the ones where no IUCN polygon exists - or are these species
  ### whose ranges only occur in cells beyond the LOICZID grid?
spp_list <- spp_list %>%
  filter(!str_detect(spatial_source, 'subpop') & !str_detect(spatial_source, 'alias')) 
spp_list <- spp_list %>%
  left_join(read.csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv'), 
                     stringsAsFactors = FALSE),
            by = 'spp_group') %>%
  left_join(spp_am %>% select(am_sid = speciesid, occurcells),
            by = 'am_sid')

>>>>

spp_list <- spp_list %>%
  mutate(sm_perc = ifelse(!is.na(sm_perc), 0, sm_perc))
  # filter(!is.na(sm_perc)) %>%
  ### will ditch the ones where no IUCN polygon exists - or are these species
  ### whose ranges only occur in cells beyond the LOICZID grid?
spp_list <- spp_list %>%
  left_join(read.csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv'), 
                     stringsAsFactors = FALSE),
            by = 'spp_group') %>%
  left_join(spp_am %>% select(am_sid = speciesid, occurcells),
            by = 'am_sid')

### 2016-02-01 manuscript-main.Rmd
updating species area calculations with the latest and greatest species list

data_file <- 'data/spp_list_w_area_trimmed.csv'
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) %>%
#  filter(!is.na(popn_category)) %>% ### filter out unassessed species
  filter(!is.na(sm_perc))           ### filter out NA maps (usually IUCN maps with no polygons)

### generate other lists

spp_all_file <- 'data/spp_all.csv'
spp_all <- read.csv(spp_all_file, stringsAsFactors = FALSE)

@@

iucn_maps_file <- 'data/spp_iucn_maps.csv'
spp_iucn_maps <- read.csv(iucn_maps_file, stringsAsFactors = FALSE) %>%
  filter(spp_group != 'hagfishes') %>%           ### not from IUCN...
  filter(sciname %in% spp_iucn_marine$sciname)   ### ditch freshwater spp

>>>>

data_file <- 'data/spp_list_w_area_trimmed.csv'
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) 
### NOTE: as of Jan 31, includes all map pairs, even ones where IUCN area == 0

### generate other lists
spp_all_file <- 'data/spp_all.csv'
spp_all <- read.csv(spp_all_file, stringsAsFactors = FALSE)

@@

iucn_maps_file <- 'data/spp_iucn_maps.csv'
spp_iucn_maps <- read.csv(iucn_maps_file, stringsAsFactors = FALSE) %>%
  filter(spp_group != 'hagfishes')           ### not from IUCN...
